| Base de datos de abejas ibéricas \n| Iberian bees database\n

### 2022-04-24 Manuscript/manuscript.Rmd
Update on table

title: "| Base de datos de abejas ibéricas \n| Iberian Bees database\n"

@@

@@

> **Iberian Bees database**. Bees are a diverse group with more than 1,000 species known from the Iberian Peninsula. They have increasingly received special attention due to their important role as pollinators and providers of ecosystem services. In addition, various rapid human-induced environmental changes are leading to the decline of some of its populations. However, we know very little about the conservation status of most species and for many species, we hardly know their true distributions across the Iberian Peninsula. Here we present a collaborative effort to collate and curate a database of Iberian bee occurrences to answer questions about their distribution, habitat preference, phenology, or historical trends. In total we have accumulated `r formatC(nrow(data),format="d", big.mark=",")` records from the Iberian Peninsula and the Balearic Islands of `r length(unique(data$Accepted_name))` different species with `r round(geo/nrow(data),2)*100`% of georeferenced records collected between `r min(data$Year, na.rm = T)` and `r max(data$Year, na.rm = T)`. In addition, each record has associated information such as the sampling location (`r round(local/nrow(data),2)*100`%), collector and person who identified the species (`r round(deter/nrow(data),2)*100`%), date of the capture (`r round(date/nrow(data),2)*100`%) and plant species where the bees were captured (`r round(flw/nrow(data),2)*100`%). We believe that this database is the starting point to better understand and conserve bee biodiversity in the Iberian Peninsula. It can be accessed at: https://doi.org/10.5281/zenodo.6354502.

# Palabras clave

> Biodiversidad; Apoidea; Anthophila; Polinizadores; Fenología

# Keywords

> Biodiversity; Apoidea; Anthophila; Pollinators; Phenology

@@

###### LEYENDA DE TABLA

@@

###### TABLE CAPTION

@@

```{r Tabla1, results='asis', echo=FALSE, cache=FALSE}
library("knitr")
metadata <- read.csv("../Data/Metadata/attributes.csv")
colnames(metadata) <- c("","Variable name", "Description", "Data type")

kable(metadata[,-1], caption ="\\textbf{Figure 1}")
```

@@

###### PIES DE FIGURA

@@

###### FIGURE LEGENDS

>>>>

title: "| Base de datos de abejas ibéricas \n| Iberian bees database\n"

@@

**Palabras clave**: Biodiversidad; Apoidea; Anthophila; Polinizadores; Fenología

@@

> **Iberian bees database**. Bees are a diverse group with more than 1,000 species known from the Iberian Peninsula. They have increasingly received special attention due to their important role as pollinators and providers of ecosystem services. In addition, various rapid human-induced environmental changes are leading to the decline of some of its populations. However, we know very little about the conservation status of most species and for many species, we hardly know their true distributions across the Iberian Peninsula. Here we present a collaborative effort to collate and curate a database of Iberian bee occurrences to answer questions about their distribution, habitat preference, phenology, or historical trends. In total we have accumulated `r formatC(nrow(data),format="d", big.mark=",")` records from the Iberian Peninsula and the Balearic Islands of `r length(unique(data$Accepted_name))` different species with `r round(geo/nrow(data),2)*100`% of georeferenced records collected between `r min(data$Year, na.rm = T)` and `r max(data$Year, na.rm = T)`. In addition, each record has associated information such as the sampling location (`r round(local/nrow(data),2)*100`%), collector and person who identified the species (`r round(deter/nrow(data),2)*100`%), date of the capture (`r round(date/nrow(data),2)*100`%) and plant species where the bees were captured (`r round(flw/nrow(data),2)*100`%). We believe that this database is the starting point to better understand and conserve bee biodiversity in the Iberian Peninsula. It can be accessed at: https://doi.org/10.5281/zenodo.6354502.

**Keywords**: Biodiversity; Apoidea; Anthophila; Pollinators; Phenology

@@

**LEYENDA DE TABLA**

@@

**TABLE CAPTION**

@@

```{r Tabla1, results='asis', echo=FALSE, cache=FALSE}
library("knitr")
#metadata <- read.csv("../Data/Metadata/attributes.csv")
library(kableExtra)

library(tidyverse)

d <- data.frame(colnames(data))
colnames(d) <- "Variable_name"

d <- reshape2::melt(d)

Description <- c("Taxonomic rank", #1
                 "Taxonomic rank",
                 "Taxonomic rank",
                 "Taxonomic rank",
                 "Accepted species name", #5
                 "Original species name",
                 "Country of collection",
                 "Province of collection",
                 "Locality as provided by orginal collectors",
                 "Geographic coordinates", #10
                 "Geographic coordinates",
                 "Accuracy of the coordinates provided by the authors",
                 "Year of collection",
                 "Month of collection",
                 "Day of collection", #15
                 "Approximate range of dates if specific dates are missing",
                 "Approximate range of dates if specific dates are missing",
                 "Name of the collector",
                 "Name of the person who identified the specimen",
                 "Number of females recorded", #20
                 "Number of males recorded",
                 "Number of workers recorded (for social species)",
                 "Number of specimens recorded without sex identification",
                 "Digital object identifier",
                 "Plant species where the specimen was collected", #25
                 "Unique identification in the local collection",
                 "All authors that have contributed on the original dataset",
                 "Extra column for additional information",
                 "Notes or queries",
                 "Unique identifier in the IberianBee database" #30
                 )

d$Description <- Description

Data_type <- c("Categorical",
               "Categorical",
               "Categorical",
               "Categorical",
               "Categorical", #5
               "Categorical",
               "Categorical",
               "Categorical",
               "Text",
               "Decimal degrees", #10
               "Decimal degrees", 
               "Text",
               "Date (YYYY)",
               "Date (MM)",
               "Date (DD)", #15
               "Date (DD-MM-YYYY)",
               "Date (DD-MM-YYYY)",
               "Categorical",
               "Categorical",
               "Natural number", #20
               "Natural number",
               "Natural number",
               "Natural number",
               "Text/link",
               "Text", #25
               "Categorical",
               "Text",
               "Text",
               "Text",
               "Categorical")

d$Data_type <- Data_type

colnames(d) <- c("Variable name", "Description", "Data type")

d$`Variable name`[d$`Variable name`=="Accepted_name"] <- "Accepted.name"

d$`Variable name`[d$`Variable name`=="Original_name"] <- "Original.name"

d$`Variable name`[d$`Variable name`=="Local_id"] <- "Local.id"

kbl(d, caption = '\\textbf{Table 1}', format = 'latex', escape = F,booktabs = T, linesep = "\\addlinespace") %>% row_spec(0, bold=T)

@@

**PIES DE FIGURA**

@@

**FIGURE LEGENDS**
